---
title: "Assignment 2"
author: "Edwin X. Garcia Rios"
date: "`r format(Sys.time(), '%Y-%b-%d, %I:%M %p')`"
output: html_document
---

# __R Tutorial: dplyr__

```{r, message=FALSE, warning=FALSE}
library(dplyr)
library(gapminder)

data(gapminder)
head(gapminder)
```

__Q1. What class is the gapminder dataset?__
```{r}
class(gapminder)
```
__Q2. Filter a section of gapminder with a life expectancy smaller than 29.__
```{r}
filter(gapminder, lifeExp < 29)
```
__Q3. Filter a section of gapminder with a life expectancy smaller than 29.__
```{r}
filter(gapminder, country == "Rwanda", year > 1979)
```
__Q4. Create a new dataset from gapminder excluding the column gdpPercap.__
```{r}
new_gapminder <- gapminder %>%
  select(-gdpPercap)
new_gapminder
```
__Q5. Arrange the dataset in ascending order of lifeExp.__
```{r}
new_gapminder %>% 
  arrange(lifeExp)
```
__Q6. Arrange the dataset in descending order of lifeExp.__
```{r}
new_gapminder %>%
  arrange(desc(lifeExp))
```
__Q7. Create a new dataset with only the columns year and lifeExp.__
```{r}
gapmndr <- gapminder %>%
  select(year, lifeExp)
gapmndr
```
__Q8. Filter the dataset for the country Cambodia and show only the columns year and lifeExp.__
```{r}
filter(gapminder, country == "Cambodia") %>%
  select(year, lifeExp)
```
__Q9. Select only the countries in Africa.__
```{r}
filter(gapminder, continent == "Africa") %>%
  select(country)
```
__Q10. Create a new column called lifeExp_months that shows life expectancy in months.__
```{r}
lifeExp_months <- gapminder %>%
  mutate(lifeExp_months = 12)
lifeExp_months %>%
  select(lifeExp_months, lifeExp, everything())
```