---
title: "Assignment 3"
author: "Edwin X. Garcia Rios"
date: "2026-10-01"
output: html_document
---

# __R Tutorial: GGPLOT__
```{r}
library(ggplot2)

data("trees")
head(trees)
```
__Q1.Create a histogram showing the distribution of Girth.__
```{r}
color = c("red")
ggplot(trees,
       aes(x = Girth)) +
  geom_histogram(bins = 31,
                 fill = color) + 
  labs(
    title = "Distribution of Girth",
    x = "Girth",
    y = "Trees"
  ) +
  theme_linedraw()
```


__Q2.Create a histogram showing the distribution of Volume.__
```{r}
color = c("red")
ggplot(trees,
       aes(x = Volume)) +
  geom_histogram(bins = 31,
                 fill = color) + 
  labs(
    title = "Ditirbution of Volume",
    x = "Volume",
    y = "Trees"
  ) +
  theme_linedraw()
```


__Q3.Create a scatterplot showing the relationship between Girth and Volume.__
```{r}
ggplot(trees,
       aes(Girth, Volume)) +
  geom_point(color = "green") +
  geom_smooth(method = "lm", se = F, color = "blue") +
  labs(
    title = "Relationship Between Tree Girth and Volume"
  ) +
  theme_bw()
```


__Q4.Use the Shapiro–Wilk test to assess whether Volume is normally distributed. Report the p-value and state whether the data are normally distributed.__
```{r}
data("trees")
shapiro.test(trees$Volume)
```
__Report:__
_Since the p-value (p = 0.003579) is <0.05, the null hypotheses is rejected, therefore the data is not normally distributed._


__Q5.Repeat the Shapiro–Wilk test for Girth. Report the p-value and state whether Girth is normally distributed.__
```{r}
data("trees")
shapiro.test(trees$Girth)
```
__Report:__
_Since the p-value (p = 0.08893) is >0.05, the null hypotheses is accepted, therefore it is determined that the data has a normal distribution._
